\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% Font options
\RequirePackage{etoolbox}
\RequirePackage[sfdefault]{FiraSans}
\RequirePackage[default]{sourcesanspro}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\hidewidth\titlerule\vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Divyanshu Yadav} \\ \vspace{8pt}
    \small Jaipur, India $|$ +91 9351532707 $|$ 
    \href{mailto:yadavdavid382@gmail.com}{\underline{yadavdavid382@gmail.com}} $|$ 
    \href{https://linkedin.com/in/divyanshu-yadav-dk1}{\underline{LinkedIn}} $|$ 
    \href{https://github.com/david1-max}{\underline{GitHub}} $|$ 
    \href{https://david1-max.github.io}{\underline{Portfolio}}
\end{center}

%-----------SUMMARY-----------
\section{Professional Summary}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven Computer Science and Artificial Intelligence student at JK Lakshmipat University with a strong foundation in full-stack web development, machine learning, and core programming. Experienced in building production-ready portals and appraisal platforms during university internships. Demonstrates leadership and communication skills developed through teaching assistantships in C and Python. Eager to leverage strong technical capabilities to drive impact as a Full-Stack Developer or Machine Learning intern.
    }}
 \end{itemize}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {JK Lakshmipat University}{Jaipur, India}
      {Bachelor of Technology in Computer Science \& Engineering (Specialization: AI)}{Expected 2028}
      \resumeItemListStart
        \resumeItem{Academic Standing: Honors List / Dean's List for academic excellence.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Core Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: Python, JavaScript (ES6+), C, C++, SQL (SQLite, MySQL)} \\
     \textbf{Web Development \& Frameworks}{: React, Node.js, Express, Flask (Python), HTML5, CSS3} \\
     \textbf{Machine Learning \& Data Science}{: Pandas, NumPy, Scikit-learn, TensorFlow/PyTorch, OpenCV, NLP} \\
     \textbf{Web Protocols \& Tools}{: WebSockets, WebRTC, REST APIs, JSON, Docker, Git/GitHub}
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Professional Experience \& Internships}
  \resumeSubHeadingListStart

    \resumeSubheading
      {JK Lakshmipat University}{Jaipur, India}
      {Full-Stack Summer Intern}{May 2026 -- July 2026}
      \resumeItemListStart
        \resumeItem{Solely architected, developed, and deployed \textbf{Samiksha}, an end-to-end feedback and performance appraisal portal using Flask and SQLite.}
        \resumeItem{Implemented secure role-based access control (RBAC) separating dashboards for students, administrative faculty, and university headers.}
        \resumeItem{Engineered the core feedback analysis engine to compute multidimensional evaluation metrics; optimized SQLite database queries and indices to reduce system query latency by 30\%.}
      \resumeItemListEnd

    \resumeSubheading
      {JK Lakshmipat University}{Jaipur, India}
      {Teaching Assistant (Python \& C)}{Aug 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Instructed weekly lab sessions on loops, functions, memory allocation, and basic data structures for a batch of over 60 undergraduate students.}
        \resumeItem{Conducted code reviews, debugged pointer arithmetic and allocation errors in C, and designed coding challenges to test programming logic.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      
      \resumeProjectHeading
        {\textbf{BubbleID-Reproduction} $|$ \emph{Mask R-CNN, OC-SORT, Deep Learning, PyTorch}}{}
        \resumeItemListStart
          \resumeItem{Replicated and benchmarked the state-of-the-art BubbleID computer vision framework used to automate heat transfer research.}
          \resumeItem{Configured and fine-tuned a Mask R-CNN network in PyTorch to perform pixel-level semantic segmentation on vapor bubble contours.}
          \resumeItem{Integrated the Observation-Centric SORT (OC-SORT) tracking algorithm to measure bubble nucleation frequencies, growth rates, departure diameters, and vertical velocities across high-speed video frames.}
        \resumeItemListEnd
        
      \resumeProjectHeading
        {\textbf{vibe-chat} $|$ \emph{React, Node.js, WebRTC, Socket.io, STUN/TURN}}{}
        \resumeItemListStart
          \resumeItem{Built a real-time messaging and peer-to-peer video conferencing application using React on the frontend and Express/Node.js on the backend.}
          \resumeItem{Designed a bi-directional signaling channel using Socket.io to manage room creation, text broadcasting, and real-time state synchronization.}
          \resumeItem{Established low-latency P2P audio/video media connections using WebRTC, utilizing STUN/TURN servers to bypass NAT firewalls.}
        \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{LeetCode Solutions} $|$ \emph{Data Structures \& Algorithms, Python}}{}
        \resumeItemListStart
          \resumeItem{Maintained a structured, publicly documented repository solving algorithm challenges (Easy/Medium) covering sliding windows, monotonic stacks, and two-pointer traversals.}
          \resumeItem{Analyzed and logged rigorous time and space complexities (Big-O notation) for every solution to ensure optimal CPU and memory usage.}
        \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{JKLU Appraisal System} $|$ \emph{Flask, SQLAlchemy, MySQL (Private Repository)}}{}
        \resumeItemListStart
          \resumeItem{Programmed key features of a performance scoring portal to automate yearly university faculty evaluations.}
          \resumeItem{Designed a normalized MySQL database schema mapping publications, patents, teaching feedback scores, and research grants.}
          \resumeItem{Developed the scoring engine to compute final appraisal points based on publication index classes (Scopus, SCI, UGC Care) and author weight coefficients.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{Certifications}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{SQL (Intermediate)} Skill Certification $|$ \emph{HackerRank (Verification: \href{https://www.hackerrank.com/certificates/62122ef2428b}{\underline{62122ef2428b}})}}{Jul 2026}
    \resumeProjectHeading
      {\textbf{Problem Solving (Basic)} Skill Certification $|$ \emph{HackerRank (Verification: \href{https://www.hackerrank.com/certificates/c4a79f66666b}{\underline{c4a79f66666b}})}}{Jul 2026}
    \resumeProjectHeading
      {\textbf{SQL (Basic)} Skill Certification $|$ \emph{HackerRank (Verification: \href{https://www.hackerrank.com/certificates/bbf6076ae8f9}{\underline{bbf6076ae8f9}})}}{Jul 2026}
    \resumeProjectHeading
      {\textbf{Python (Basic)} Skill Certification $|$ \emph{HackerRank (Verification: \href{https://www.hackerrank.com/certificates/7fdc5f0187af}{\underline{7fdc5f0187af}})}}{Jul 2026}
    \resumeProjectHeading
      {\textbf{Programming with C++} $|$ \emph{Simplilearn on Coursera (Verification: \href{https://coursera.org/verify/XEBPREKSD9H2}{\underline{XEBPREKSD9H2}})}}{Jun 2025}
    \resumeProjectHeading
      {\textbf{Python Data Structures} $|$ \emph{University of Michigan on Coursera (Verification: \href{https://coursera.org/verify/1VDHAXLCXG9R}{\underline{1VDHAXLCXG9R}})}}{Dec 2024}
    \resumeProjectHeading
      {\textbf{Programming for Everybody (Python)} $|$ \emph{University of Michigan on Coursera (Verification: \href{https://coursera.org/verify/02EE3KE7V869}{\underline{02EE3KE7V869}})}}{Dec 2024}
  \resumeSubHeadingListEnd

%-----------AWARDS & ACTIVITIES-----------
\section{Awards \& Activities}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Academic Honors}{: Consistently recognized on the Dean's List / Honors List for outstanding academic performance.} \\
     \textbf{Extracurriculars}{: Active squad player for the JKLU Cricket Team, competing in inter-university tournaments.}
    }}
 \end{itemize}

\end{document}
